---
title: "607 Assignment 1"
author: "John Kellogg"
date: "8/29/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Assignment Task:  

1.Study the dataset and the associated description of the data (i.e. “data dictionary”).   
2. Create a data frame with a subset of the columns.    
 + Include the column that indicates edible or poisonous and three or four other columns.
3. Add meaningful column names  
4. Replace the abbreviations used in the data—for example  
5. Deliverable is the R code to perform these transformation tasks.  
  
  
  
#### Data Import and initial setup:  
```{r}
Mushroom_data<-read.csv(url("https://archive.ics.uci.edu/ml/machine-learning-databases/mushroom/agaricus-lepiota.data"))
Mushroom<- as.data.frame(Mushroom_data)
names(Mushroom) = c("CONSUMABLE", "CAP_SHAPE", "CAP_SURFACE", "CAP_COLOR", "BRUISES", "ODOR", "GILL_ATTACHMENT", "GILL_SPACING", "GILL_SIZE", "GILL_COLOR", "STALK_SHAPE", "STALK_ROOT", "STALK_SURFACE_ABOVE_RING", "STALK_SURFACE_BELOW_RING", "STALK_COLOR_ABOVE_RING", "STALK_COLOR_ABOVE_RING", "VEIL_TYPE", "VEIL_COLOR", "RING_NUMBER", "RING_TYPE", "SPORE_PRINT_COLOR", "POPULATION", "HABITAT")
Mushroom[] <- lapply(Mushroom, as.character)
```
#### Modifying CONSUMABLE
```{r}
Mushroom$CONSUMABLE[Mushroom$CONSUMABLE == "e"] <- "edible"
Mushroom$CONSUMABLE[Mushroom$CONSUMABLE == "p"] <- "poisonous"
```
#### Modifying Cap Shape
```{r}
Mushroom$CAP_SHAPE[Mushroom$CAP_SHAPE == "b"] <- "bell"
Mushroom$CAP_SHAPE[Mushroom$CAP_SHAPE == "x"] <- "convex"
Mushroom$CAP_SHAPE[Mushroom$CAP_SHAPE == "C"] <- "conical"
Mushroom$CAP_SHAPE[Mushroom$CAP_SHAPE == "f"] <- "flat"
Mushroom$CAP_SHAPE[Mushroom$CAP_SHAPE == "k"] <- "knobbed"
Mushroom$CAP_SHAPE[Mushroom$CAP_SHAPE == "s"] <- "sunken"
```
#### Modifying Odor
```{r}
Mushroom$ODOR[Mushroom$ODOR == "a"] <- "almond"
Mushroom$ODOR[Mushroom$ODOR == "l"] <- "anise"
Mushroom$ODOR[Mushroom$ODOR == "c"] <- "creosote"
Mushroom$ODOR[Mushroom$ODOR == "y"] <- "fishy"
Mushroom$ODOR[Mushroom$ODOR == "f"] <- "foul"
Mushroom$ODOR[Mushroom$ODOR == "m"] <- "musty"
Mushroom$ODOR[Mushroom$ODOR == "n"] <- "none"
Mushroom$ODOR[Mushroom$ODOR == "p"] <- "pungent"
Mushroom$ODOR[Mushroom$ODOR == "s"] <- "spicy"
```
#### Modifying Population
```{r}
Mushroom$POPULATION[Mushroom$POPULATION == "a"] <- "abundant"
Mushroom$POPULATION[Mushroom$POPULATION == "c"] <- "clustered"
Mushroom$POPULATION[Mushroom$POPULATION == "n"] <- "numerous"
Mushroom$POPULATION[Mushroom$POPULATION == "s"] <- "scattered"
Mushroom$POPULATION[Mushroom$POPULATION == "v"] <- "several"
Mushroom$POPULATION[Mushroom$POPULATION == "y"] <- "solitary"
```
#### Modifying Habitat
```{r}
Mushroom$HABITAT[Mushroom$HABITAT == "g"] <- "grasses"
Mushroom$HABITAT[Mushroom$HABITAT == "l"] <- "leaves"
Mushroom$HABITAT[Mushroom$HABITAT == "m"] <- "meadows"
Mushroom$HABITAT[Mushroom$HABITAT == "p"] <- "paths"
Mushroom$HABITAT[Mushroom$HABITAT == "u"] <- "urban"
Mushroom$HABITAT[Mushroom$HABITAT == "w"] <- "waste"
Mushroom$HABITAT[Mushroom$HABITAT == "d"] <- "woods"

```
### Results: 

```{r, echo=FALSE}
Mushroomset1<- subset(Mushroom, select = c(CONSUMABLE,CAP_SHAPE,ODOR,POPULATION,HABITAT))
summary(Mushroomset1)
head(Mushroomset1, n=20)
```


